\input book

\centerline{\bf Together}
\centerline{\it Sunday, 2017/04/02}



\vfill
\break


﻿The nightmares, relentless.  ``Look down, and deal with it'' had
become a pragmatic ritual of survival \break among the psychotic tools of
that trade.  Everything in my power.  Lots of power of collaboration,
lots of rotational inertia.  Lots of chaos, too.  Somehow my inner
consciousness was the winning approach.  Leave the head of outer
consciousness in that psycho bucket and let the inner consciousness
express and find and walk.  Served all purposes.  Self defense and
preservation and evolution.  On the superficial plane of existence I
was exhausted.  And toying with methods of rage and anger in the
appearances around me, on the street, in the mud of the gutters beside
the avenues that ``people'' walk.  On a deeper level I was productive
and restful and living, but the consciousness was not in this
mind-body identity, it was -- critically and painfully -- elsewhere,
with another.  With my wife, Gwyneth.


I have no idea how she has managed it.  How we have managed it.  The
problem begs the quantum entanglement of consciousness (QEC).


Perhaps not so much more than faith and discipline, commitment,
applied to extraordinary circumstances.


However, in all fairness, we believe in the QEC.  It's a ridiculously
open and vague notion, scientifically.  But we need an explanation of
such magnitude to settle the intellectual questioning of experience.


There have been many phenomena external to our couple which we've been
quite pointed about excluding from our ``discipline''.  Awakening to
the significance of this matter, too.


\vfill
\break


﻿It had laid within me like a supernatural thing, his little film about
his daughter's career in the performing arts.  The import, a broadband
message from across space-time.  A point of contact precious to me,
and substantial.  More than having met the man, it was a father's wish
for his daughter's future success.  A piece of art, a family
adventure, a touchstone that my mind and soul could ingest and digest
and regest.  Film school.


Mad skills.  Look out, world, here comes Gwyneth.


As a name becomes a prayer.


\vfill
\break


﻿Boys, at least this one, grow up with the expectation that a wedding
is an emotional white out.  Devastating.  And by natural implication,
to be avoided at all costs.  Girls, by all accounts, grow up expecting
to survive such events.


We've been dreaming of our wedding.  I've been dreaming of carrying my
babies around on my back in a papoose.  My wife, a famous actor and
performer, has a serious talent for programming my dreams.  Of course,
I'm extremely open to her suggestions, being in love with her.  Dreams
of the experiential categories are common in this context.  I avoid
speaking for her, complicated business, that.  But it's my
understanding that she's in, well over her head, as well.


\vfill
\break


﻿I don't know how it's possible.  The match must be as two protons
sharing two electrons.  As important as the discovery of
extraterrestrial life.  That's our couple.  $H_{2}$.  The quantum
entanglement of consciousness.


It's kind of scary.  What happens when we meet?  Will there be an
event?  Will spacetime collapse into a Minkowski Void?


No!  Of course not.  I hope to be kissed, and to remember to kiss, in
return -- if I'm kissed.


\vfill
\bye
