\input preamble-png

﻿The nightmares, relentless.  ``Look down, and deal with it'' had
become a pragmatic ritual of survival \break among the psychotic tools of
that trade.  Everything in my power.  Lots of power of collaboration,
lots of rotational inertia.  Lots of chaos, too.  Somehow my inner
consciousness was the winning approach.  Leave the head of outer
consciousness in that psycho bucket and let the inner consciousness
express and find and walk.  Served all purposes.  Self defense and
preservation and evolution.  On the superficial plane of existence I
was exhausted.  And toying with methods of rage and anger in the
appearances around me, on the street, in the mud of the gutters beside
the avenues that ``people'' walk.  On a deeper level I was productive
and restful and living, but the consciousness was not in this
mind-body identity, it was -- critically and painfully -- elsewhere,
with another.  With my wife, Gwyneth.


I have no idea how she has managed it.  How we have managed it.  The
problem begs the quantum entanglement of consciousness (QEC).


Perhaps not so much more than faith and discipline, commitment,
applied to extraordinary circumstances.


However, in all fairness, we believe in the QEC.  It's a ridiculously
open and vague notion, scientifically.  But we need an explanation of
such magnitude to settle the intellectual questioning of experience.


There have been many phenomena external to our couple which we've been
quite pointed about excluding from our ``discipline''.  Awakening to
the significance of this matter, too.

\bye
