\input book

\centerline{\bf Together}
\centerline{\it Wednesday, 2017/03/29}



\vfill
\break

﻿We were born twins out of a galactic collision.  We tell or say
absolutely anything to each other, in private.  We share a confidence
inviolable.  It is less an invention and more a demand we place each
on the other.  What I need from you I know I will get from you,
contained in that inviolable spiritual ether of the subjective
metaphysical dynamic of the infinite love of the internal fountain of
energy.

\vfill
\break

﻿On that journey, the path of the bear, my mind was lost to the stars.
With gravel in my eyes I looked in every direction for a method of
self preservation.  I looked to the forest by imagining, and found
that my level of consciousness was more powerful than my level of
intellect.  I went to the spirit world, following the ancestors, and
found friends there.  Eventually I returned from the path of the bear
as my psychological state of being accepted the place I found itself
in.

\vfill
\break

﻿It is this freedom, the freedom to express all things of this
existence, that we share.  It is this freedom that we value, cherish,
defend, and breathe in this union.  It is this freedom that we express
so dearly.

Is this art?  It is more than science, the subjective that contains
the objective, and in this sense it is art.  As the art of life in
honor and breath it is blood, first, and art, second.

\vfill
\break

﻿In this joining all myths are dispelled, including the mythology of
insecurity and infidelity.

Worlds of thought and meaning dancing under the sky.

Worlds of metaphor and intent.  Worlds of words and images.  Breath.

Voice.  First, the awareness of voice.  Second, the practice of
interaction.  Third, the finding of voice.  \break Fourth, the practice of
interaction.

In the sky, clouds of thought condense to intent and purpose and
expression, meaning, understanding, reflection.  Significance.
Substance.

Sometimes the easiest way to describe speech is as food.  Sweet or
sour, positive or inert and unsigned, or perhaps negative.  Protein,
cake, salad, celery, or soup.  Perhaps stew.

Joined, a tether of varying qualities.  Some, distinct.  Others,
fluid.

\vfill
\break

We have established the knowing of knowledge, the sense of language,
the finding of comprehension, and the holding of belief.

The language of mathematics combines the disciplines of learning with
the senses for the suspension and discovery of meaning to discreet
points.

The languages of art combines the disciplines of learning with the
senses for the suspension and discovery of meaning to continuous lines
and threads.


\vfill
\bye
